Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-04 inc/gun/gun_design.tex
tweak on gun_design

The acceleration region of our prototype UEM system has several features which are unique in comparison to standard electron guns.
As discussed in Chapter \ref{chap:considerations}, notable requirements for a UEM electron gun include the need to handle a large photoemission area and yet to retain all of the electrons, it may not employ a pin-hole to selectively clean the electron beam.
These necessities lead to several additional criteria.
The system must first be able to accept the large laser spot size needed to generate the electron beam.
Then, in order to accomodate this large electron pulse, both the cathode Wehnelt and anode aperture must be similarly large; in fact, the beam size at the anode aperture will typically be larger than at the emission source due to transverse beam expansion during acceleration.
Also, care must be taken to ensure a relatively uniform electric field for acceleration of the pulse.
While in transit from the cathode to the anode, this large beam is more susceptable to non-uniformities in the electic field given that it will span a wider proportion %TODO andreas wrote "larger <<something unreadable>>"
of the acceleration region than the thin beams used in conventional TEM.

>>>>

The acceleration region of our prototype UEM system has several features which are unique in comparison to standard electron guns.
As discussed in Chapter \ref{chap:considerations}, notable requirements for a UEM electron gun include the need to handle a large photoemission area and yet to retain all of the electrons, it may not employ a pin-hole to selectively clean the electron beam.
These necessities lead to several additional criteria.
The system must first be able to accept the large laser spot size needed to generate the electron beam.
Then, in order to accomodate this large electron pulse, both the cathode Wehnelt and anode aperture must be similarly large; in fact, the beam size at the anode aperture will typically be larger than at the emission source due to transverse beam expansion during acceleration.
Also, care must be taken to ensure a relatively uniform electric field for acceleration of the pulse.
While in transit from the cathode to the anode, this large beam is more susceptable to non-uniformities in the electic field given that it will span a larger volume of the acceleration region than the thin beams used in conventional TEM.
